Application-Level Regression Testing Framework using Jenkins

### 2017-03-08 manuscript/manuscript.tex
added Best Practices section
Best Practices section draft

>>>>

\section{Best Practices}
\begin{itemize}
\item Tests are developed on the JYC development rack and not assigned into a Jenkins tab until reviewed.
\item Email notification is enabled for most tests and the field is always populated with a test owner.
\item All tests contain a description that describes what is tested, resources required, scheduling frequency, and overall summary  to be readable by the management team.
\item Log file count is limited in the test configuration to keep from filling filesystem space with verbose logs.
\item Tests are coded to be more verbose than necessary so that failures can be isolated quickly and easily.
\end{itemize}
